\begin{description}

\item[TP or TP3] {Team Project 3, a compulsory Level 3 Computing
    Science module where students are required to produce some piece
    of software. In our case, this system.}

\item[GitHub] {Refers to the website \url{github.com} which
    hosts the git repository for our project's documentation and
    implentation at \url{https://github.com/Dan-McElroy/Team-Project--Q}}

\item[Git] {A version control system used by Team Q to keep
    track of all digital files related to the system. Not to be
    confused with the term of `endearment' in the English language.}

\item[Portability] {A system which is portable is able to be used on a
    different computer to the one on which it was developed with no,
    or minimal, changes.}

\item[pdf] {A file format used to display documents.}

\item[LaTeX] {A document mark-up language used for all project documentation.}

\item[PCR] {Polymerase chain reaction, a biochemical technology used to amplify pieces of DNA by several orders of magnitude, creating copies of a particular DNA sequence.}

\item[Primer] {A strand that serves as a starting point for DNA synthesis.}

\item[Java] {An object-oriented computer programming language.}

\item[IDE] {An integrated development environment.}

\item[Netbeans] {An IDE for developing primarily in Java.}

\item[Eclipse] {An IDE for developing primarily in Java.}

\item[Swing] {The primary Java GUI widget toolkit.}

\item[JavaFX] {A software platform for creating applications.}

\item[GUI] {Graphical User Interface, an interface which a user interacts with using images.}

\item [PC] {Personal Computer, the terminals which the application will be run on.}

\item [DNA] {Deoxyribonucleic acid, a molecule that contains the genetic instructions used in the functioning of living organisms and many viruses.}

\item [Base] {The a,t,g and c symbols that comprimise a DNA sequence.}

\item [Nucleotide] {Biological molecules that form the building blocks of nucleic acids.}

\item [NCBI] {National Center for Biotechnology Information, a branch of the National Institudes of Health. From their website, users retrieve DNA sequences.}
\end{description}
