%- 3 objects, Sequence, Primer, TestResult
%Basic in construction, all classes have toStrings and booleans.


The models used in the application are few in number and very simple, BLAH BLAH BLAH BLAH

We used three model classes, Primer, TestResult and Sequence.

\paragraph{Primer}
The Primer class is purely designed to test user-designed primers. It has one attribute, \verb£code£, the String representing the user's primer
which is tested against in the primer test methods, which make up the remainder of the primer. The class is primarily made up of methods designed
to test \verb£code£ against the various rules described in Section \ref{intro:prelims}. The method \verb£test()£ gathers runs all above test methods
and returns a larger TestResult, indicating if the user's Primer is adequate outside of the larger context of the sequence.

\paragraph{TestResult}
TestResult is a class used to format the output of one or multiple primer tests. TestResult uses an enumerated type called PassState with values
\verb£PASS£, \verb£FAIL£ and \verb£CLOSEFAIL£, the last of which describes a state where the primer's value from a test lies outside of the recommended
values, but is close enough to a pass to be acceptable, provided this is only the state of a minority of tests. TestResult uses two ArrayLists, one of
PassStates (\verb£passes£) and another of Strings (\verb£out£), to keep track of the state and informative message to be displayed to the user for each test. Its methods are concerned with concatenating results into larger TestResults. \verb£perfect()£ will return true if all entries in \verb£passes£ equal a \verb£PASS£.
\verb£adequate()£, the method that is checked to gate the user's access past the Primer Selection panel returns false if any of the tests returned \verb£{FAIL}£,
or if more than 60\% returned \verb£CLOSEFAIL£, and returns true otherwise.

%Sequence:
%2 strings to represent each strand of the sequence, ints to represent the start and end of the desired PART of that sequence, 2 Primer objects.
%
%Complement method taking a base and returning its complement, isUnique tests if primer is unique (durr), tempDifference compares the temperature
%of both primers, primerTest combines all methods that return a TestResult and produce an overall TestResult, the toString of which should be
%shown in the Primer Evaluation Dialog.
\paragraph{Sequence}
This class contains two Strings, \verb£oStrand£ and \verb£cStrand£, representing the strand of DNA that the user took in and the ''complementary'' strand that
is generated when the sequence is constructed. Integers \verb£start£ and \verb£end£ represent the indexes of the start and end of the selected area in the
sequence.
